---
graphics: yes
output:
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
    keep_tex: true
  pdf_document:
    toc: no
    keep_tex: true
  bookdown::html_document2:
    fig_caption: yes
    toc: no
  word_document: default
bibliography:
- Ch2_citations.bib
- R_Citations.bib
header-includes: \usepackage{setspace}\doublespacing \usepackage{lineno} \usepackage{placeins}
---

\begin{center}
Supplementary Material for:
	
\textbf{\Large Social-ecological models with social hierarchy and spatial structure applied to small scale fisheries}
	
\textsc{Sophie Wulfing$^{1*}$ and Easton R. White$^{1}$\\}
\vspace{3 mm}
\normalsize{\indent $^1$Department of Biological Sciences, University of New Hampshire, 03824, NH, USA\\}
$\text{*}$ Corresponding authors: Sophie Wulfing (SophieWulfing@gmail.com) and Dr. Easton White (Easton.White@unh.edu)
\end{center}

\pagebreak


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, dev="cairo_pdf", cache = TRUE)

library(deSolve)
library(tidyverse)
library(ggplot2)
library(gridExtra)
library(kableExtra)
library(FME)
library(ggpubr)
library(gridtext)


#setwd("C:/Users/sophi/Documents/GitHub/UNH_Docs/Proposal/Soc_Ecol_Model")

```

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```
\linenumbers

Equations 2), 4), and 5) are as follows:

\begin{equation}
\tag{2}
\frac{dX_i}{dt} = k_iX_i(1-X_i)[U_{A,i} - U_{B,i}]
\end{equation}

\begin{equation}
\tag{4}
U_{A,i} = \frac{1}{(F_i + c_i)} + d_iX_i + \rho_i X_j
\end{equation}

\begin{equation}
\tag{5}
U_{B,i} = \omega_i + d_i(1-X_i) + \rho_i(1-X_j)
\end{equation}

Substituting equations 4) and 5) into equation 2 Gives:

$\frac{dX_i}{dt} = k_iX_i(1-X_i)[\frac{1}{(F_i + c_i)} + d_iX_i + \rho_i X_j - \omega_i - d_i(1-X_i) - \rho_i(1-X_j)]$

$\frac{dX_i}{dt} = k_iX_i(1-X_i)[\frac{1}{(F_i + c_i)} - \omega_i + d_i(X_i-1+X_i) + \rho_i(X_j-1+X_j)]$

$\frac{dX_i}{dt} =  k_iX_i(1-X_i) [\frac{1}{F_i+c_i} - \omega_i + d_i(2X_i - 1) + \rho_i(2X_j - 1)]$

<!-- # Inside vs. Outside social influence with symmetry -->
```{r modelSetup}
params_list <- data.frame(r_1 = 0.16, s_1 = 0.8, h_1 = .25, k_1 = 0.17, w_1 = 1.44, c_1 = 0.5, d_1 = 0.3, m_1 = 0, rho_1 = 0,
                          r_2 = 0.16, s_2 = 0.8, h_2 = .25, k_2 = 0.17, w_2 = 1.44, c_2 = 0.5, d_2 = 0.3, m_2 = 0, rho_2 = 0)

xstart <- c(F_1 = 0.406, F_2 = 0.406, X_1 = .24, X_2 = .24)
timespan <- seq(from = 0, to = 1000, by = 1)


Bauch.Coupled <- function (t, y, params) {
  ## first extract the state variables
  F_1 <- y[1] #Fish Pop var
  F_2 <- y[2] #Fish Pop var
  X_1 <- y[3] #conservationist var
  X_2 <- y[4] #conservationist var

  #TT <- y[5]
  
  ## now extract the parameters
  r_1 <- params["r_1"] # Net growth/fecundity
  s_1 <- params["s_1"] # supply and demand
  h_1 <- params["h_1"] # Harvesting efficiency
  k_1 <- params["k_1"] # Social learning rate
  w_1 <- params["w_1"] # conservation costs
  c_1 <- params["c_1"] # rarity valuation param
  d_1 <- params["d_1"] # social norm strength
  m_1 <- params["m_1"] # Inflow of fish from pop 2 to pop 1
  rho_1 <- params["rho_1"] # Influence of pop 2 on pop 1
  
  r_2 <- params["r_2"] # Net growth/fecundity
  s_2 <- params["s_2"] # supply and demand
  h_2 <- params["h_2"] # Harvesting efficiency
  k_2 <- params["k_2"] # Social learning rate
  w_2 <- params["w_2"] # conservation costs
  c_2 <- params["c_2"] # rarity valuation param
  d_2 <- params["d_2"] # social norm strength 
  m_2 <- params["m_2"] # Inflow of fish from pop 1 to pop 2
  rho_2 <- params["rho_2"] # Influence of pop 1 on pop 2
  
  ## now code the model equations
  dF_1dt <-  r_1 * F_1 * (1-F_1) - (h_1 * F_1 * (1-X_1))/(F_1+s_1) - m_2 * F_1 + m_1 * F_2
  dF_2dt <-  r_2 * F_2 * (1-F_2) - (h_2 * F_2 * (1-X_2))/(F_2+s_2) - m_1 * F_2 + m_2 * F_1
  
  dX_1dt <- k_1 * X_1 * (1-X_1) *(1/(F_1 + c_1) - w_1 + d_1*(2*X_1 - 1) + rho_1 * (2*X_2 - 1))
  dX_2dt <- k_2 * X_2 * (1-X_2) *(1/(F_2 + c_2) - w_2 + d_2*(2*X_2 - 1) + rho_2 * (2*X_1 - 1))
  
  ## combine results into a single vector
  dydt <- c(dF_1dt, dF_2dt, dX_1dt, dX_2dt)
  ## return result as a list!
  
  list(dydt)
}

params_Bauch2 <- params_list

times <- timespan
xstart <- c(F_1 = 0.406, F_2 = 0.406, X_1 = .24, X_2 = .24)

ode(
  func=Bauch.Coupled,
  y=xstart,
  times=times,
  parms=params_Bauch2
) %>%
  as.data.frame() -> out_Coupled
```

```{r influenceBoth, warning = FALSE, fig.cap = "With symmetry conditions, $d$ and $\rho$ have the same effect", eval = FALSE}

timespan <- seq(from = 0, to = 1000, by = 1)

rhoparams <- c(0.01, 0.05, 0.1, 0.5)
dparams <- c(0.01, 0.05, 0.1, 0.5)
plotList <- list()
k <- 0

for(i in 1:length(dparams)){
  params_Default <- params_list
  params_Default[7] <- dparams[i]
  params_Default[16] <- dparams[i]
  
  for(j in 1:length(rhoparams)){
    k <- k+1
    params_Default[9] <- rhoparams[j]
    params_Default[18] <- rhoparams[j]
  
   times <- timespan
    xstart <- c(F_1 = 0.406, F_2 = 0.406, X_1 = .24, X_2 = .24)

    ode(
      func=Bauch.Coupled,
      y=xstart,
      times=times,
      parms=params_Default
    ) %>%
      as.data.frame() -> out_Diff

    p <- out_Diff %>%
      gather(variable,value,-time) %>%
      ggplot(aes(x=time,y=value,color=variable))+
      geom_line(size=1)+
      theme_classic()+
      labs(x='time (yr)',y='pop') +
      theme(legend.position = "none") +
      ggtitle(paste("d = ", params_Default[7], "rho = ", params_Default[9])) +
      theme(plot.title = element_text(size=7))
    plotList[[k]] <- p
  }
}

  
  do.call("grid.arrange", c(plotList, ncol=4))

```
